**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2020-11-30 paper/paper.Rmd
Fun with distill metadata
https://rstudio.github.io/distill/metadata.html

---
title: "**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**"
date: '`r Sys.Date()`'
author:
  - name: "Kelly L. Sovacool"
    url: https://github.com/kelly-sovacool
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan, Ann Arbor, MI
    orcid_id: 0000-0003-3283-829X
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https
---

>>>>

---
title: "**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**"
date: '`r Sys.Date()`'
author:
  - name: "Kelly L. Sovacool"
    url: https://github.com/kelly-sovacool
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan, Ann Arbor, MI
    orcid_id: 0000-0003-3283-829X
  - name: "Sarah L. Westcott"
    url: https://github.com/mothur-westcott
    affiliation: Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
  - name: "M. Brodie Mumphrey"
    url: https://github.com/MBMumphrey
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan, Ann Arbor, MI
  - name: "Gabrielle A. Dotson"
    url: https://github.com/dotsonga
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan, Ann Arbor, MI
  - name: "Patrick D. Schloss"
    url: https://github.com/pschloss
    affiliation: Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
bibliography: references.bib
output:
  pdf_document:
    keep_tex: false
    includes:
      in_header: header.tex
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
creative_commons: CC BY-SA
twitter:
  creator: "@kelly_sovacool"
  site: "@PatSchloss"
---
